Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
more

For benchmarks, we gathered a set of 245 benchmarks from two sources, which we will refer to as {\bench isa} and {\bench leon}.
The first ({\bench isa}) consists of the 79 benchmarks from the Isaplanner benchmark suite~\cite{DBLP:conf/itp/JohanssonDB10} that do not contain higher-order functions.
The benchmarks have been used recently as challenge problems for a variety of inductive theorem provers.
These benchmarks heavily involve recursive functions, and are limited to the combined theory of uninterpreted functions and inductive datatypes.
The second ({\bench leon}) consists of 166 benchmarks from the Leon repository~\footnote{Available at \url{https://github.com/epfl-lara/leon}.},
which were constructed from verification conditions from simple Scala programs.
These benchmarks also heavily involve recursive functions over inductive datatypes,
and also cover a wide variety of theories, including bitvectors, arrays, and linear and non-linear arithmetic.
Each of the 245 benchmarks are of the form described in formula~(\ref{eq:wdf}) from Section~\ref{sec:prelim},
in particular they each are a conjoined list of function definitions followed by a (negated) conjecture.
A majority of these benchmarks are unsatisfiable, although a handful of the benchmarks in the {\bench leon} set are satisfiable.

@@

\begin{figure}[t]
\centering
{
\begin{tabular}{|l|cc|cc|cc|cc|l|cc|cc|cc|cc|}
\hline
  & \multicolumn{2}{c|}{{\bench z3}}     & \multicolumn{2}{c|}{{\bench cvc4}}     & \multicolumn{2}{c|}{{\bench cvc4+f}}     & \multicolumn{2}{c|}{{\bench cvc4+i}}     & & \multicolumn{2}{c|}{{\bench z3}}     & \multicolumn{2}{c|}{{\bench cvc4}}     & \multicolumn{2}{c|}{{\bench cvc4+f}}     & \multicolumn{2}{c|}{{\bench cvc4+i}}
\\
  & u & s & u & s & u & s & u & s & & u & s & u & s & u & s & u & s
\\
\hline
{\bench isa} & 14  & 0 & 15  & 0 & 15  & 0 & {\win 61}  & 0 & {\bench isa+w} & 15  & 0 & 15  & 0 & 15  & 0 & 14  & 0
\\
{\bench leon}  & 73  & 0 & 80  & 0 & 80  & 0 & {\win 96}  & 0 & {\bench leon+w}  & 78  & 2 & 80  & 0 & 76  & {\win 9} & 78  & 0
\\
{\bench isa+m} & 17  & 0 & 18  & 0 & 18  & 0 & {\win 44}  & 0 & {\bench isa+mw}  & 18  & 35  & 18  & 0 & 18  & {\win 153} & 17  & 0
\\
{\bench leon+m}  & 83  & 11  & 103 & 6 & 104 & 6 & {\win 117} & 6 & {\bench leon+mw} & 98  & 75  & 98  & 6 & 95  & {\win 169} & 98  & 6
\\
\hline
{\bench total} & 187 & 11  & 216 & 6 & 217 & 6 & {\win 318} & 6 & {\bench total} & 209 & 112 & 211 & 6 & 204 & {\win 331} & 207 & 6
\\
\hline
\end{tabular}
\\
}
\caption{Number of unsat and sat responses for of all configurations on benchmarks
before and after the translation $\conv$.}
\label{fig:results}
\end{figure}

>>>>

We gathered a set of 245 benchmarks from two sources, which we will refer to as
{\bench isa} and {\bench leon}. The first ({\bench isa}) consists of the 79
benchmarks from the Isaplanner benchmark
suite~\cite{DBLP:conf/itp/JohanssonDB10} that do not contain higher-order
functions. The benchmarks have been used recently as challenge problems for a
variety of inductive theorem provers. These benchmarks heavily involve
recursive functions, and are limited to the combined theory of uninterpreted
functions and inductive datatypes. The second ({\bench leon}) consists of 166
benchmarks from the Leon repository,\footnote{%Available at
\url{https://github.com/epfl-lara/leon}} which were constructed from
verification conditions from simple Scala programs. These benchmarks also
heavily involve recursive functions over inductive datatypes, and also cover a
wide variety of theories, including bitvectors, arrays, and linear and
non-linear arithmetic. Each of the 245 benchmarks are of the form described in
formula~(\ref{eq:wdf}) from Section~\ref{sec:prelim}.
% in particular they each
%are a conjoined list of function definitions followed by a (negated)
%conjecture.
A majority of these benchmarks are unsatisfiable, although a
handful of the benchmarks in the {\bench leon} set are satisfiable.

@@

\begin{figure}[t]
\centering
{
\begin{tabular}{|l|cc|cc|cc|cc|l|cc|cc|cc|cc|}
\hline
  & \multicolumn{2}{c|}{{\bench z3}}     & \multicolumn{2}{c|}{{\bench cvc4}}     & \multicolumn{2}{c|}{{\bench cvc4+f}}     & \multicolumn{2}{c|}{{\bench cvc4+i}}     & & \multicolumn{2}{c|}{{\bench z3}}     & \multicolumn{2}{c|}{{\bench cvc4}}     & \multicolumn{2}{c|}{{\bench cvc4+f}}     & \multicolumn{2}{c|}{{\bench cvc4+i}}
\\
  & u & s & u & s & u & s & u & s & & u & s & u & s & u & s & u & s
\\
\hline
{\bench isa} & 14  & 0 & 15  & 0 & 15  & 0 & {\win 61}  & 0 & {\bench isa+w} & 15  & 0 & 15  & 0 & 15  & 0 & 14  & 0
\\
{\bench leon}  & 73  & 0 & 80  & 0 & 80  & 0 & {\win 96}  & 0 & {\bench leon+w}  & 78  & 2 & 80  & 0 & 76  & {\win 9} & 78  & 0
\\
{\bench isa+m} & 17  & 0 & 18  & 0 & 18  & 0 & {\win 44}  & 0 & {\bench isa+mw}  & 18  & 35  & 18  & 0 & 18  & {\win 153} & 17  & 0
\\
{\bench leon+m}  & 83  & 11  & 103 & 6 & 104 & 6 & {\win 117} & 6 & {\bench leon+mw} & 98  & 75  & 98  & 6 & 95  & {\win 169} & 98  & 6
\\
\hline
{\bench total} & 187 & 11  & 216 & 6 & 217 & 6 & {\win 318} & 6 & {\bench total} & 209 & 112 & 211 & 6 & 204 & {\win 331} & 207 & 6
\\
\hline
\end{tabular}
\\
}
\caption{\,Number of unsat (u) and sat (s) responses for of all configurations on benchmarks
before and after the translation $\conv$}
\label{fig:results}
\end{figure}
